EpisoPass: Password Management based on Episodic Memories

### 2016-12-11 paper/Password2016/dlj.tex
...

If we want to avoid having to carry any special device for authentication,
either we must used some form of biometrics, or all the information required 
for the authentication must be
must be stored in the user's memory.
%
However, the biggest problem with memory-based authentication is that
users cannot reliably remember passwords or master password that are long and complex enough to be secure.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on a user's episodic memories. This has the benefit that unlike a password, a person is highly unlikely to forget such episodic memories.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We therefore propose \textit{EpisoPass}, a password manager that generates strong passwords
based only on a user's secret and unforgettable episodic memories.

@@

EpisoPass is a password manager that supports the generation of
strong passwords based on a user's secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
% Memories in human brain are not uniform.
Our brains store numerous memories, but different memories have different characteristics.
Some memories are very short-lived, while others are recallable for long periods of time.
When we have a particularly impressive experience,
the memory of it will stay in our mind for a long time and can't be easily forgotten.
On the other hand, other topics are more difficult to remember. For example, when studying mathematics and trying to remember a new formula,
it can be hard to memorize without significant practice,
since knowledge of the formula is unrelated to
any personal experiences.
The former type of memory is called an {\it episodic\/} memory and most people find such
memories easy to recollect and hard to forget.
Memories of passwords belong in the latter category. People find them
hard to remember and easy to forget, in the same way people find it difficult
to remember mathematical formulas.

@@

\begin{figure}
\centering
% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
\caption{Generating an Amazon password with EpisoPass.}
\label{web1}
\end{figure}

\marginnote{You mention that episodic memories and cognitive passwords have been used in the past, but it's not clear to me (from the text here) why your system is different. Perhaps you could put a sentence or two about this?}

The idea of using episodic memories for authentication has a long history and early papers suggested using episodic memories for creating passwords. Authentication using secret questions is sometimes referred to as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches have been used as an alternative to password-based authentication systems.
%
% However, conversion from episodic memories to password strings
% was not studied at all.

@@

\begin{enumerate}
\item A user registers multiple question texts related to their own personal
secret unforgettable episodic memories. For each question they must provides
a single correct answer and multiple additional incorrect answers.

@@

\item EpisoPass shows the questions and answers to the user allowing
them to select the correct answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates a
strong password candidate string.
After selecting all of the correct answers,
the user copies the calculated string
and registers it as the password for the service.
\end{enumerate}

\subsection{Using EpisoPass in a browser}

Figure \ref{web1} shows how to generate a password
on EpisoPass running in a browser by accessing the EpisoPass site.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for a question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections. If incorrect answers are chosen the wrong password will be generated. On the other hand, when the user selects the correct answers for all of the questions,
the correct password is calculated and shown at the top of the page.

@@

In Figure \ref{web1},
``\textsf{Amazon123456}'' is provided as the seed string,
and based on the selections to the ten questions,
the seed string is converted to the string
``\textsf{Tblgeq808187}'',
to be used as the password for Amazon.com.

When the user clicks on different candidate answers 
the seed string is converted to a completely different strings, such as
``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.

In this way, different selections yield different password strings and
the unique password string generated after selecting the correct answers should be
used as the password for the service.

Capital letters in the seed string are substituted for capital letters in the password,
and digits in the seed string are substituted for digits. In this way
the generated password can be arranged to conform with any password character restrictions
the site might impose.

The first question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the question with a photo at the bottom is related to a more recent event
which the author believes he will never forget.
All the questions are based on the author's episodic memories that he's unlikely to ever forget,
and that he believes nobody else will know the correct answer for.

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
\caption{Selecting a different set of answers.}
\label{web11}
\end{figure}

Usability has been considered as a key consideration, and the questions 
and answers in the figures can be edited directly in the browser. They can be
saved on the server by clicking the ``save to server'' button or saved locally
if the user prefers.
While the Q-A data sets are saved, no information about the correct answer or the
generated password is saved on the server. Consequently there is no requirement for the user
to trust the server to keep the data secret.
The Q-A data can be downloaded to the user's local machine in JSON format 
by clicking the ``save to file'' button. To upload the data back to the server, the user
simply drags the JSON file to the EpisoPass page.

When the secret string is changed to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, the user can generate different passwords for
different services just by changing the seed string.

\begin{figure}
  \centering
%  \includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
  \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
  \caption{Generating a new password for Facebook.}
  \label{web2}
\end{figure}

Character substitution is performed based on the value
calculated by hashing a concatenation of all the questions and selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
as the answer to the question ``\textbf{\texttt{Who's the bully?}}'',
a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for calculating the hash value.

The last question in Figure \ref{web1} is not intended as a secret question based on an
episodic memory, but is instead a question
for generating different passwords for different situations.
By providing a question like this, the user can generate completely different passwords
for different months and years, say.

@@

\marginnote{Is the Android app generated as a unique app for each user? If so, I think it's worth making this clear.}
If a user prefers not to use the EpisoPass service on the Web,
there is an alternative EpisoPass application for Android
which requires no network connection.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top of the page.
The application is compiled and built on the server and contains
all of the information needed for the particular user to
generate passwords using the Q-A sets entered.

When the user runs the application and selects the correct answer
to each question, the password will be generated in the same way as
on the site, as shown in Figures \ref{android1} and \ref{android2}.
This can then be copied to the password entry for access
to a particular service.

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
\caption{Running EpisoPass on Android.}
\label{android1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
\caption{After finishing selections.}
\label{android2}
\end{figure}

The calculation is performed on Android without the need for a network connection,
so the user can safely generate passwords without being concerned about an
attacker observing any data transfer.

@@

One of the difficulties of the previous two approaches is that the user 
must re-type or copy the password string into the service's password
field after it's been generated.
This isn't ideally convenient, so we have also developed a browser 
extension that allows EpisoPass to be used directly with the login
page of services on the Web.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
\caption{Using EpisoPass on the login window.}
\label{extension}
\end{figure}

A browser extension is a JavaScript add-on program which runs
on top of existing Web pages.
%
Figure \ref{extension} shows the login page of Amazon.com, with the 
EpisoPass questions automatically overlaid directly onto the page
by the browser extension.
%
When the user accesses the Amazon login page,
the browser extension automatically runs on the page,
acquires the questions and answers from the EpisoPass server,
and displays them using the same style as for the Android application.
%
After answering all of the questions, a password is calculated from the
selected answers and automatically pasted into the password field of the page
by the extension. In this way users can log in to various services just by
answering the questions presented, and without even seeing the password string.
It appears as if the EpisoPass-based authentication is being provided directly
by the services themselves.

\section{Discussion}

In this section, we discuss the advantages and potential disadvantages of using EpisoPass.

@@

\marginnote{The fact that an `old' memory is unlikely to be forgotten is perhaps obvious, but this could be a good place
to cite a paper on memory/psychology about this if you're aware of any?}

The biggest advantage of using EpisoPass is that
users don't have to remember strong password strings.
%
The seed string and question-answer data is essentially public,
and users of EpisoPass can save them wherever is convenient. They can
then easily generate passwords by running
EpisoPass and answering the questions.
If a question is based on old unforgettable episodic memory,
there is little chance of losing the password for a service
as long as the seed string and questions are available.
If the user's memory is related to an episode that took place 20 years ago, say, and the user clearly
still remembers the episode now, it is unlikely the episode will be forgotten in the future.

@@

\marginnote{In the comments you mention that ``generating service-specific unique seed string is not trivial''. I think this is worth mentioning in the paper.}

In the previous examples showing the author's EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings were chosen because they are easily memorable.
In practice any seed string could be used as the seeds for the various services,
and automatic generation of seed strings is a possibility.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
%
\marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is considerably more than a billion (closer to 10 thousand billion, (US) or 10 million million (UK).}
%
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over a billion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of the questions is key to using EpisoPass effectively.
If the episode is shared by someone else,
this other person might easily be able to answer the question and generate the
user's password.
%
The episode related to each question should therefore not be known to any other person,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first, but our experience
has been that we try to remember such experiences from our personal past,
we can soon recall many trivial episodes which are unforgettable but
nonetheless not important to other people.
%
The following list shows some examples of experiences that we believe make good candidates for
EpisoPass questions.

\begin{itemize}
\item Memories of very minor injuries that nobody would have cared about apart from you.

\item Memories of bad experience such as embarrassing blunders or failures, especially in the case where
it was never admitted to anyone else.

\item Experiences of finding inconsequential but special items which only you are interested in.
\end{itemize}

For example, a question such as
``who hit you when you were six years old?''
is about a trivial experience that most people would never have reason to discuss,
but an experience that may have been unpleasant at the time is hard to forget.

Questions such as ``Which food do you like best?'' should be avoided,
since friends or family might know the user's tastes, thereby allowing 
others to select the correct answer.
Questions related to an episode which the user is proud of should also be
avoided, since this is a something the user might prefer to discuss with others.

We don't usually talk about trivial bad experiences with other people,
but we might boast about good experiences (some might even write blog posts about them).
Similarly our tastes ({\it e.g.\/} favorite foods) might change in the long run.
Using such episodes for questions should therefore be avoided.

@@

It can be difficult to provide a large number of false answers to a question like
``what is your favorite sport?''
because the number of possible answers is limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is straightforward.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S. as possible answers.

In this way, false answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks
\cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
We can use such systems to provide a list of potential false answers almost automatically.

@@

Although everyone has to make use of authentication systems, not everyone
is good at handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is unintuitive and remembering complex
passwords is hard.
%
Using EpisoPass, people can use password-based systems without having to invent
techniques for creating and remembering strong passwords. The Q-A configuration step
is a one-time process, after which the system becomes straightforward to use.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
required for the service.
%
Our experience of using browser extensions suggests that
this approach offers the most seamless experience.

\subsection{Password requiring frequent updates}

Many services still require users to change passwords periodically in an attempt
to strengthen security.
%
Although this is no longer considered good-practice, since humans struggle to
generate a stream of strong passwords \cite{Schneier:change}, the practice is
still widespread.
%
% A user can generate a new strong password by using a random character generator
% on a password manager, but he might want to old passwords in case some trouble happens.
%
Using EpisoPass, users can provide a date-related question
similar to that shown as the final question in Figure \ref{web1}. This allows
different strong passwords to be generated depending on the answer chosen
for this question. Using this technique, people can easily manage both old and new 
passwords efficiently.

>>>>

If we want to avoid having to carry any special device for authentication,
all the information required for the authentication should be
kept in the users' brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories that they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user cannot forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
% Memories in human brain are not uniform.
We keep various memories in our brain, but different memories have different natures.
Some memories are very short-lived, and others remain for a long time.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a new formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.

@@

The idea of using episodic memories for authentication has a long history.
Early papers suggested using episodic memories for creating passwords.
Authentication by using secret questions,
sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
has long been used as an
alternative to password-based authentication systems.
%
% However, conversion from episodic memories to password strings
% was not studied at all.

@@

\begin{enumerate}
\item A user registers many question texts related to the user's personal
secret episodic memories that the user never forgets,
and provides a correct answer and additional fake answers.

@@

\item EpisoPass shows the data to the user so that
the user can select the right answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates
strong password candidate strings.
After selecting all the right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

\begin{figure}[H]
\centering
% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
\caption{Generating an Amazon password with EpisoPass.}
\label{web1}
\end{figure}

\subsection{Using EpisoPass on a browser}

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections.
When the user selects the correct answers to all the questions,
the right password is calculated and shown at the top.

@@

In Figure \ref{web1},
``\textsf{Amazon123456}'' is provided as the seed string,
and according to the selections to the five questions,
the seed string is converted to a string
``\textsf{Tblgeq808187}'',
which can be used as the password for Amazon.com.

When the user clicks another candidate,
the seed string is converted to another strings like
``\textsf{Xvdkzb940345}'' (Figure \ref{web11}).

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
\caption{Selecting a different answer.}
\label{web11}
\end{figure}

In this way, different selections yields different password strings and
the password string generated after selecting correct answers can be
used as the password for the service.

Capital letters in the seed string are substituted to capital letters in the password,
and digits in the seed string are substituted to digits,
so that generated passwords conforms to password character restrictions
sometimes requested by the service.

The first question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the question with a photo at the bottom is related to a more recent event
which the author believes he will never forget.
All the questions are based on the author's episodic memories
that he thinks he never forgets, and he believes that
nobody else knows which one of the candidate is the right answer.

Questions and answers can be edited directly on the browser, and they can be
saved on the server by clicking the ``save to server'' button.
The Q-A data sets are saved on the server,
but no information about the correct answer or the
generated password is saved on the server.
The Q-A data in JSON format can be downloaded to the local machine
by clicking the ``save to file'' button.
the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.

When we change the secret string to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, we can generate different passwords for
different services just by changing the seed string.

\begin{figure}[H]
  \centering
%  \includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
  \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
  \caption{Generating the password for Facebook.}
  \label{web2}
\end{figure}

Character substitution is performed based on the hash value
calculated from concatenating all the questions and selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
to the question ``\textbf{\texttt{Who's the bully?}}'',
a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for calculating the hash value.

The last question in Figure \ref{web1} is not a secret question, but a question
for generating different passwords for different situations.
By providing such a question, users can generate completely different passwords
for different months and years, for example.

@@

If a user doesn't like to use the EpisoPass service on the Net,
he can use an EpisoPass application on Android
which does not use network connections.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top.
The application contains all the information required for generating passwords.
(The application is compiled and built on the server.)

When the user runs the application and selects the correct answer
to each question, he can eventually get the password and copy it to the password entry.
(Figure \ref{android1},\ref{android2})

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
\caption{Running EpisoPass on Android.}
\label{android1}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
\caption{After finishing selections.}
\label{android2}
\end{figure}

The calculation is performed on Android without network connection,
and the user can safely generate passwords 
without feeling the fear of being observed by attackers.

@@

When a user use the EpisoPass service or the EpisoPass application,
he has to type or copy the password string after generating the password.
Since it is not convenient,
we provide a browser extension for using EpisoPass on the login window of
various Web services.

A browser extension is a JavaScript add-on program which runs
on top of existing Web pages.
%
Figure \ref{extension} shows the login page of Amazon.com, with which
EpisoPass questions are automatically displayed by the browser extension.
%
Here, when the Amazon login page is accessed from the browser,
the browser extension program automatically runs on the page,
acquires questions and answers from the EpisoPass server,
and shows them to the user just the same way as the Android application.
%
After answering all the questions, a password is calculated from the
selected answers and pasted to the password field of the page.
Using the extension, users can login to various services just by
answering questions, without seeing any password string.
It looks as if these services are offering
EpisoPass-based authentication.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
\caption{Using EpisoPass on the login window.}
\label{extension}
\end{figure}

\section{Discussions}

In this section, we discuss the advantages and caveats of using EpisoPass.

@@

The biggest advantage of using EpisoPass is that
users don't have to remember strong password strings.
%
Users of EpisoPass can save the seed string and question-answer data
at any place, and easily generate passwords by running
EpisoPass and answering questions.
If the question is based on old unforgettable episodic memories,
there is little chance of losing passwords
as long as the seed string and the questions are available.
If the user's memory is related to an episode of 20 years ago and the user clearly
remembers the episode now, it is unlikely that he forgets the episode 10 years later.

@@

In the previous examples showing the author's EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings are used because they are easily memorable.
Of course any seed string can be used as seeds for various services,
and automatic generation of seed strings is possible.

@@

The strength of the generated password depends on the number of
questions and the secret level of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but the strength of secret questions has not been studied enough.
%
When we use 10 secret questions with 20 answers and
there's no clue for the answer,
1 billion ($20^{10}$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
It is almost the same entropy as using random 8-character English alphabets
as a password, in which case the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of the questions is the key to using EpisoPass.
If the episode is shared by someone else,
that person can easily answer the question and generate the
password just like the user.
%
The episode related to each question should not be known to other people,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first, but
when we try to remember experiences of old days,
we can recall many trivial episodes which are unforgettable but
not important to other people.
%
Old experiences like the following are candidates for
good questions used in EpisoPass.

\begin{itemize}
\item Memory of small injury. (Nobody cares it but you.)

\item Memories of bad experience like blunders or defeat.
(You don't tell it to anybody.)

\item Experience of finding a small special item which only you are interested in.
\end{itemize}

For example, a question like
``who hit you when you were 6 years old?''
is about a trivial experience that people do not mention,
but a bad experience like this is not forgettable.

Questions like ``Which food do you like best?'' should be avoided,
since some of the friends might know the user's taste.
Questions related to an episode which the user is proud of should also be
avoided, since the user might talk about the episode to somebody else.

We usually don't tell our bad trivial experiences to other people,
but we might boast of good experiences or even write a blog about it.
Also, our tastes (e.g. favorite food) might change in the long run.
Using such episodes for questions should be avoided.

@@

It is difficult to provide enough number of fake answers to a question like
``what was your favorite sport?''
because the number of possible answers are limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is easy.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S.

In this way, fake answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks%
\cite{Huang:2012:LFC:2426725.2426728}% 
\cite{BooWa}% Boo!Wa!
\cite{Wang:2007:LSE:1441428.1442086}.
Using such systems, we can get a list of fake answers almost automatically.

@@

Although everyone has to use authentication systems on the Internet these days,
not all the people are good at handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is not intuitive and
people forget passwords very easily.
%
Using EpisoPass, people can use password-based systems without knowing
techniques for creating and remembering strong passwords.
They only have to provide
questions and answers based on secret episodic memories.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
required for the service.
%
Our experience of using browser extensions suggests that
this approach is worth consideration.

\subsection{Frequent password update}

On many services, users are requested to change passwords periodically
to strengthen security.
%
Such a practice is not recommended these days
because humans cannot create strong passwords frequently\cite{Schneier:change}.
%
% A user can generate a new strong password by using a random character generator
% on a password manager, but he might want to old passwords in case some trouble happens.
%
Using EpisoPass, users can just provide a date-related question
like the last question shown in Figure \ref{web1},
and generate different strong passwords based on the answer.
Using this technique, people can easily manage old and new passwords.
